Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-07 R/model_persistence_check.Rmd
Update

Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany

<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
<br>
ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
<br>
[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
<br>
GitHub: [markus1bauer](https://github.com/markus1bauer)

Persistence sensu Wilsey (2021) Restor Ecol [DOI: 10.1111/rec.13132](https://doi.org/10.1111/rec.13132)

@@

```{r}
get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
            seed_density + substrate_depth +
            (1 | site/plot),
          data = sites)
ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 10)) +
  expand_limits(y = 0) + ggtitle("Normal distribution")
ggplot(data = data.frame(x = c(-40, 40)), aes(x = x)) +
  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 10)) +
  expand_limits(y = 0) + ggtitle("Cauchy distribution")
ggplot(data.frame(x = c(-40, 40)), aes(x = x)) +
  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 10)) +
  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
```

@@

@@

```{r}
mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
  theme(axis.text.x = element_text(angle = 90))
mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
  theme(axis.text.x = element_text(angle = 90))
```

>>>>

Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany
<br/>
<br/>
<span>&#42;</span> Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)

ORCiD ID: [0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
<br>
[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
<br>
GitHub: [markus1bauer](https://github.com/markus1bauer)

Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)

Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)

Analysis guided by
<br>
Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
<br>
Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
<br>
Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
<br>
Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)

@@

@@

```{r}
get_prior(n ~ target_type + exposition + sand_ratio + survey_year_fct +
            seed_density + substrate_depth +
            (1 | site/plot) + (1 | botanist_year),
          data = sites)
ggplot(data = data.frame(x = c(0, 1)), aes(x = x)) +
  stat_function(fun = dbeta, n = 101, args = list(shape1 = 3.5, shape2 = 2.2)) +
  expand_limits(y = 0) +
  ggtitle("Beta distribution for Intercept")
ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = .2)) +
  expand_limits(y = 0) +
  ggtitle("Normal distribution for treatments")
ggplot(data = data.frame(x = c(-.4, .4)), aes(x = x)) +
  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
  expand_limits(y = 0) +
  ggtitle("Cauchy distribution") # See Lemoine 2019 https://doi.org/10.1111/oik.05985
ggplot(data.frame(x = c(-.4, .4)), aes(x = x)) +
  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
  expand_limits(y = 0) +
  ggtitle(expression(Student~italic(t)*"-distribution")) # Software standard
```

@@

```{r}
mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncolumn = 2))
mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncolumn = 2))
mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
  theme(axis.text.x = element_text(angle = 45))
mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
  theme(axis.text.x = element_text(angle = 45))
```
